Indexes measures for oak decline severity using phenotypic descriptors

### 2019-09-12 manuscript/manuscript.Rmd
added word count, spelling and grammar checks

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache = TRUE)
```

@@

```{r prep}
source('../code/data_prep.R')
```

@@

# Figures

```{r site_differences,fig.cap='Site differences',fig.height=6}
source('../code/site_differences.R')
grid.arrange(site_differences$a,site_differences$b,nrow = 1)
```

```{r descriptor_adjustment,fig.cap='Error bars show ±1SE of the mean.\nDashed red line shows the overall mean.'}
source('../code/descriptor_adjustment.R')
descriptor_adjustment %>%
  wrap_plots()
```

```{r DI_space,fig.cap=''}
DIspace()
```

```{r descriptor_contributions, fig.cap = ''}
source('../code/descriptor_contributions.R')
descriptor_contributions %>%
  wrap_plots() + 
  plot_annotation(title = 'Descriptor importance scores from random forest models for relative contributions to\ndecline index measures',caption = 'Gini importance scores averaged across 100 repetitions')
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

@@

```{r check}
source('../code/check.R')
check()
```
